`r title`

### 2017-12-11 lib/report.Rmd
progress

@@

```{r search_conducted_plot}
search_conducted_plot
```

@@

```{r contraband_found_plot}
contraband_found_plot
```

```{r contraband_found_by_race_plot}
contraband_found_by_race_plot
```

```{r citation_issued_plot}
citation_issued_plot
```

```{r arrest_made_plot}
arrest_made_plot
```

@@

\newpage
```{r missing_columns_added_table}
missing_columns_added_table
```

@@

>>>>

```{r by_year_by_hour_of_day, fig.height = 10}
by_year_by_hour_of_day_plot
```

@@

@@

Search conducted: `r search_conducted_pct`

Contraband found: `r contraband_found_pct`

Citation issued: `r citation_issued_pct`

Arrest made: `r arrest_made_pct`

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
citation_issued_by_race_plot
arrest_made_by_race_plot
```

@@

@@

```{r missing_columns_added_table}
missing_columns_added_table
```
